---
output:
  html_document: default
  pdf_document: default
  word_document: default
---
1.
```{r}
library(MASS)
train = read.table("pima_train.txt", header = TRUE)
test = read.table("pima_test.txt", header = TRUE)
lda.fit = lda(type ~ npreg + glu + bp + skin + bmi + ped + age, data = train)
lda.pred = predict(lda.fit, test)
mean(lda.pred$class != test$type)
```

2.
```{r}
table(lda.pred$class, test$type)
```

```{r}
29 / (29 + 39)     #patients with diabetes misclassified as healthy
18 / (114 + 18)    #healthy patients misclassified as having diabetes
```
Patients with diabetes misclassified as healthy are more common than healthy patients are misclassified as having diabetes in the test data.

3.
```{r}
qda.fit = qda(type ~ npreg + glu + bp + skin + bmi + ped + age, data = train)
qda.pred = predict(qda.fit, test)
mean(qda.pred$class != test$type)
```

4.
```{r}
table(qda.pred$class, test$type)
```
```{r}
25 / (25 + 43)     #patients with diabetes misclassified as healthy
25 / (107 + 25)    #healthy patients misclassified as having diabetes
```

Although LDA model has lower misclassification error on the provided test set, it classifies more patients with diabetes as healthy(lda:0.43, qda:0.37) which is very dangerous to the patients and the health organisation would not like to see.

5.
```{r}
glm.fit = glm(type ~ npreg + glu + bp + skin + bmi + ped + age, data = train, family = binomial)
glm.probs = predict(glm.fit, test, type = "response")
dim(test)
```
```{r}
dim(train)
```
```{r}
mean(train$type == 1)    # find the prior probability
```

```{r}
glm.pred = rep(0, 200)
glm.pred[glm.probs > 0.3283133] = 1
mean(glm.pred != test$type)
```
Fit the logistic regression model on train model, the test error is 0.24.

6.
find the coefficients:
```{r}
summary(glm.fit)
```

use the predict function first
```{r}
predict(glm.fit, newdata = data.frame(npreg=5, glu=111, bp=81, skin=33, bmi=25.1, ped=0.36, age=48), type="response")
```

Calculate the diabetes status:
find the odd first
```{r}
glm.fit$coefficients %*% matrix(c(1, 5, 111, 81, 33, 25.1, 0.36, 48), nrow=8)
```
```{r}
exp(-1.669107)/(1+exp(-1.669107))
```
So the predicted diabetes status by logistic regression is 0.1585433.
